---
title: "3. Analysis"
author: "Boy Remmelzwaal"
date: "7/1/2021"
output: html_document
---

In this document you can find the script used to calculate the RMSE of the imputations. You can also find the script used to calculat the raw bias, coverage rate, confidence interval of the regression coefficients. Finally this script covers the code used to calculate the reverse model bias.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(mice)
library(dplyr)
library(magrittr)
library(readr)
library(purrr)
library(mvtnorm)
library(tidyr)
library(tibble)

```


# True data
```{r}

# Fitting the model to the data, selectin coefficeints
truemodel <- data %$% 
  lm(BMI ~ Glucose + BloodPressure + SkinThickness + Insulin) %>% 
  coef()

# Reverse model bias - Fitting the predictors as the outcome variable 
truedata.fit.x1y <- lm(Glucose ~ BMI + BloodPressure + SkinThickness + Insulin, data = data)$coefficients
truedata.fit.x2y <- lm(BloodPressure ~ Glucose + BMI + SkinThickness + Insulin, data = data)$coefficients
truedata.fit.x3y <- lm(SkinThickness ~ Glucose + BloodPressure + BMI + Insulin, data = data)$coefficients
truedata.fit.x4y <- lm(Insulin ~ Glucose + BloodPressure + SkinThickness + BMI, data = data)$coefficients
```


# Function: grab results
```{r}


# Function for grabbing the results for multiple imputation methods
grab.it <- function(x){
  model <- x %>% 
    map(~.x %>%
        complete("all") %>%
        map(~.x %$%
              lm(BMI ~ Glucose + BloodPressure + SkinThickness + Insulin)) %>%
        pool())
  estim <- model %>%
        map(~.x %>% summary() %>% .$estimate) %>%
        do.call(rbind, args = .)
  model %>%
  map(~.x %>% .$pooled %>%
        mutate(se = sqrt(diag(var(estim))),
               lower = estimate - qt(.975, df) * se,
               upper = estimate + qt(.975, df) * se,
               bias = estimate - truemodel,
               CIW = upper - lower,
               coverage = lower <= truemodel & truemodel <= upper) %>% 
              column_to_rownames(var = "term")) %>%
    Reduce("+", .) / nsim
}


# Function for grabbing the results for single imputation methods
grab.it.single <- function(x){
  model <- x %>% 
    map(~.x %>%
          complete("all") %>%
          map(~.x %$%  
                lm(BMI ~ Glucose + BloodPressure + SkinThickness + Insulin)) %>% 
          pool())
  estim <- model %>% 
    map(~.x %>% coefficients()) %>% 
    do.call(rbind, args = .)
  df <- model[[1]]$df.residual
  model %>% map(~.x %>% summary() %>% .$coefficients %>% as.data.frame() %>% 
        mutate(se = sqrt(diag(var(estim))),
               lower = Estimate - qt(.975, df) * se,
               upper = Estimate + qt(.975, df) * se,
               bias = Estimate - truemodel,
               CIW = upper - lower,
               coverage = lower <= truemodel & truemodel <= upper)) %>% 
    Reduce("+", .) / nsim
}
```


## Function: reverse model regression coefficients (true values) - Bias.
```{r}


true.estimates.p <- function(x) {

      fit <- lm(BMI ~ Glucose + BloodPressure + SkinThickness + Insulin, data = x)
      summary <- summary(fit, conf.int = TRUE)

      #betas
      x1.beta <- fit$coefficients["Glucose"]
      x2.beta <- fit$coefficients["BloodPressure"]
      x3.beta <- fit$coefficients["SkinThickness"]
      x4.beta <- fit$coefficients["Insulin"]

      
      #standard errors
      x1.beta.se <- summary$coefficients["Glucose", "Std. Error"]
      x2.beta.se <- summary$coefficients["BloodPressure", "Std. Error"]
      x3.beta.se <- summary$coefficients["SkinThickness", "Std. Error"]
      x4.beta.se <- summary$coefficients["Insulin", "Std. Error"]

      #CI low 
      x1.beta.CI.low <-  confint(fit)[2,1]
      x2.beta.CI.low  <- confint(fit)[3,1]
      x3.beta.CI.low  <- confint(fit)[4,1]
      x4.beta.CI.low  <- confint(fit)[5,1]
      
      #CI high
      x1.beta.CI.high <-  confint(fit)[2,2]
      x2.beta.CI.high  <- confint(fit)[3,2]
      x3.beta.CI.high  <- confint(fit)[4,2]
      x4.beta.CI.high  <- confint(fit)[5,2]
      
      # AW
      x1.beta.aw <- x1.beta.CI.high - x1.beta.CI.low
      x2.beta.aw <- x2.beta.CI.high - x2.beta.CI.low
      x3.beta.aw <- x3.beta.CI.high - x3.beta.CI.low
      x4.beta.aw <- x4.beta.CI.high - x4.beta.CI.low
      
      #bias
      x1.beta.bias <- 0
      x2.beta.bias <- 0
      x3.beta.bias <- 0
      x4.beta.bias <- 0
      
      #coverage 
      x1.beta.coverage <- FALSE
      x2.beta.coverage <- FALSE
      x3.beta.coverage <- FALSE
      x4.beta.coverage <- FALSE
       
      r.squared <- summary$r.squared
      
      #reversed models
      fit.x1y <- lm(Glucose ~ BMI + BloodPressure + SkinThickness + Insulin, data = x)
      fit.x2y <- lm(BloodPressure ~ Glucose + BMI + SkinThickness + Insulin, data = x)
      fit.x3y <- lm(SkinThickness ~ Glucose + BloodPressure + BMI + Insulin, data = x)
      fit.x4y <- lm(Insulin ~ Glucose + BloodPressure + SkinThickness + BMI, data = x)
   
      #summaries
      summary.x1y <- summ(fit.x1y, confint = TRUE)
      summary.x2y <- summ(fit.x2y, confint = TRUE)
      summary.x3y <- summ(fit.x3y, confint = TRUE)
      summary.x4y <- summ(fit.x4y, confint = TRUE)

      #betas
      x1y.beta <- fit.x1y$coefficients["BMI"]
      x2y.beta <- fit.x2y$coefficients["BMI"]
      x3y.beta <- fit.x3y$coefficients["BMI"]
      x4y.beta <- fit.x4y$coefficients["BMI"]
      
      #standard errors
      x1y.beta.se <- summary(fit.x1y)$coefficients[2,2]
      x2y.beta.se <- summary(fit.x2y)$coefficients[3,2]
      x3y.beta.se <- summary(fit.x3y)$coefficients[4,2]
      x4y.beta.se <- summary(fit.x4y)$coefficients[5,2]
   
      #CI low 
      x1y.beta.CI.low <- summary.x1y$coeftable[2,2]
      x2y.beta.CI.low  <- summary.x2y$coeftable[3,2]
      x3y.beta.CI.low  <- summary.x3y$coeftable[4,2]
      x4y.beta.CI.low  <- summary.x4y$coeftable[5,2]
      
      #CI high
      x1y.beta.CI.high <- summary.x1y$coeftable[2,3]
      x2y.beta.CI.high  <- summary.x2y$coeftable[3,3]
      x3y.beta.CI.high  <- summary.x3y$coeftable[4,3]
      x4y.beta.CI.high  <- summary.x4y$coeftable[5,3]
      
      # AW
      x1y.beta.aw <- x1y.beta.CI.high - x1y.beta.CI.low
      x2y.beta.aw <- x2y.beta.CI.high - x2y.beta.CI.low
      x3y.beta.aw <- x3y.beta.CI.high - x3y.beta.CI.low
      x4y.beta.aw <- x4y.beta.CI.high - x4y.beta.CI.low
  
      #bias
      x1y.beta.bias <- 0
      x2y.beta.bias <- 0
      x3y.beta.bias <- 0
      x4y.beta.bias <- 0
        
      #coverage 
      x1y.beta.coverage <- FALSE
      x2y.beta.coverage <- FALSE
      x3y.beta.coverage <- FALSE
      x4y.beta.coverage <- FALSE
      

  return(c(x1.beta, x1.beta.se, x1.beta.bias, x1.beta.aw, x1.beta.coverage, r.squared,
           x2.beta, x2.beta.se, x2.beta.bias, x2.beta.aw, x2.beta.coverage,
           x3.beta, x3.beta.se, x3.beta.bias, x3.beta.aw, x3.beta.coverage,
           x4.beta, x4.beta.se, x4.beta.bias, x4.beta.aw, x4.beta.coverage,
           x1y.beta, x1y.beta.se, x1y.beta.bias, x1y.beta.aw, x1y.beta.coverage,
           x2y.beta, x2y.beta.se, x2y.beta.bias, x2y.beta.aw, x2y.beta.coverage, 
           x3y.beta, x3y.beta.se, x3y.beta.bias, x3y.beta.aw, x3y.beta.coverage, 
           x4y.beta, x4y.beta.se, x4y.beta.bias, x4y.beta.aw, x4y.beta.coverage))
}


```

## Function: reverse model regression coefficients (imputations) - Bias.
```{r}


statistics.p <- function(x) {
   
   m <- x$m # Amount of imputations
   
   #  Get the truedata from the global environment
   truedata.fit <- get("truemodel", envir = .GlobalEnv)
   truedata.x1y <- get("truedata.fit.x1y", envir = .GlobalEnv)
   truedata.x2y <- get("truedata.fit.x2y", envir = .GlobalEnv)
   truedata.x3y <- get("truedata.fit.x3y", envir = .GlobalEnv)
   truedata.x4y <- get("truedata.fit.x4y", envir = .GlobalEnv)
   
   # multiple imputation analysis
   if (m > 1) {
      
      fit <- with(x, lm(BMI ~ Glucose + BloodPressure + SkinThickness + Insulin))
      est <- pool(fit)
      summary <- summary(est, conf.int = TRUE)

      
      # Betas
      x1.beta <- summary$estimate[2] # Glucose
      x2.beta <- summary$estimate[3] # BloodPressure
      x3.beta <- summary$estimate[4] # SkinThickness
      x4.beta <- summary$estimate[5] # Insulin
      
      # SE
      x1.beta.se <- summary$std.error[2]
      x2.beta.se <- summary$std.error[3]
      x3.beta.se <- summary$std.error[4]
      x4.beta.se <- summary$std.error[5]
              
      # Confidence interval low
      x1.beta.CI.low <- summary  %>% filter(term == "Glucose") %>% select(c(`2.5 %`)) %>% unlist()
      x2.beta.CI.low <- summary  %>% filter(term == "BloodPressure") %>% select(c(`2.5 %`)) %>% unlist()
      x3.beta.CI.low <- summary  %>% filter(term == "SkinThickness") %>% select(c(`2.5 %`)) %>% unlist()
      x4.beta.CI.low <- summary  %>% filter(term == "Insulin") %>% select(c(`2.5 %`)) %>% unlist()
      
      # Confidence interval high
      x1.beta.CI.high <- summary %>% filter(term == "Glucose") %>% select(c(`97.5 %`)) %>% unlist()
      x2.beta.CI.high <- summary %>% filter(term == "BloodPressure") %>% select(c(`97.5 %`)) %>% unlist()
      x3.beta.CI.high <- summary %>% filter(term == "SkinThickness") %>% select(c(`97.5 %`)) %>% unlist()
      x4.beta.CI.high <- summary %>% filter(term == "Insulin") %>% select(c(`97.5 %`)) %>% unlist()
      
      # Average width 
      x1.beta.aw <- x1.beta.CI.high - x1.beta.CI.low
      x2.beta.aw <- x2.beta.CI.high - x2.beta.CI.low
      x3.beta.aw <- x3.beta.CI.high - x3.beta.CI.low
      x4.beta.aw <- x4.beta.CI.high - x4.beta.CI.low
  
      # Raw bias
      x1.beta.bias <- x1.beta - truedata.fit["Glucose"]
      x2.beta.bias <- x2.beta - truedata.fit["BloodPressure"]
      x3.beta.bias <- x3.beta - truedata.fit["SkinThickness"]
      x4.beta.bias <- x4.beta - truedata.fit["Insulin"]
                              
      # Coverage rate
      x1.beta.coverage <- x1.beta.CI.low < truedata.fit["Glucose"] & truedata.fit["Glucose"] < x1.beta.CI.high
      x2.beta.coverage <- x2.beta.CI.low < truedata.fit["BloodPressure"] & truedata.fit["BloodPressure"] < x2.beta.CI.high
      x3.beta.coverage <- x3.beta.CI.low < truedata.fit["SkinThickness"] & truedata.fit["SkinThickness"] < x3.beta.CI.high
      x4.beta.coverage <- x4.beta.CI.low < truedata.fit["Insulin"] & truedata.fit["Insulin"] < x4.beta.CI.high
   
       # R2
      r.squared <- pool.r.squared(est, adjusted = FALSE)[[1]]
      
      # Reversing the predictor, x as outcome
      fit.x1y <- with(x, lm(Glucose ~ BMI + BloodPressure + SkinThickness + Insulin)) #Glucose as outcome
      fit.x2y <- with(x, lm(BloodPressure ~ Glucose + BMI + SkinThickness + Insulin)) #Bloodpressure as outcome
      fit.x3y <- with(x, lm(SkinThickness ~ Glucose + BloodPressure + BMI + Insulin)) #SkinThickness as outcome
      fit.x4y <- with(x, lm(Insulin ~ Glucose + BloodPressure + SkinThickness + BMI)) #SkinThickness as outcome
      
      # Pooling the new models
      est.x1y <- pool(fit.x1y)
      est.x2y <- pool(fit.x2y)
      est.x3y <- pool(fit.x3y)
      est.x4y <- pool(fit.x4y)
      
      # Summaries of models
      summary.x1y <- summary(est.x1y, conf.int = TRUE)
      summary.x2y <- summary(est.x2y, conf.int = TRUE) 
      summary.x3y <- summary(est.x3y, conf.int = TRUE)
      summary.x4y <- summary(est.x4y, conf.int = TRUE) 
   
      # Betas of Y BMI as predictor in reversed models
      x1y.beta <- est.x1y$pooled$estimate[2]
      x2y.beta <- est.x2y$pooled$estimate[3]
      x3y.beta <- est.x3y$pooled$estimate[4]
      x4y.beta <- est.x4y$pooled$estimate[5]
      
      # SE
      x1y.beta.se <- summary.x1y$std.error[2]
      x2y.beta.se <- summary.x2y$std.error[3]
      x3y.beta.se <- summary.x3y$std.error[4]
      x4y.beta.se <- summary.x4y$std.error[5]
      
      # CI LOW
      x1y.beta.CI.low <- summary.x1y  %>% filter(term == "BMI") %>% select(c(`2.5 %`)) %>% unlist()
      x2y.beta.CI.low <- summary.x2y  %>% filter(term == "BMI") %>% select(c(`2.5 %`)) %>% unlist()
      x3y.beta.CI.low <- summary.x3y  %>% filter(term == "BMI") %>% select(c(`2.5 %`)) %>% unlist()
      x4y.beta.CI.low <- summary.x4y  %>% filter(term == "BMI") %>% select(c(`2.5 %`)) %>% unlist()
      
      # CI High
      x1y.beta.CI.high <- summary.x1y  %>% filter(term == "BMI") %>% select(c(`97.5 %`)) %>% unlist()
      x2y.beta.CI.high <- summary.x2y  %>% filter(term == "BMI") %>% select(c(`97.5 %`)) %>% unlist()
      x3y.beta.CI.high <- summary.x3y  %>% filter(term == "BMI") %>% select(c(`97.5 %`)) %>% unlist()
      x4y.beta.CI.high <- summary.x4y  %>% filter(term == "BMI") %>% select(c(`97.5 %`)) %>% unlist()
    
      # AW
      x1y.beta.aw <- x1y.beta.CI.high - x1y.beta.CI.low
      x2y.beta.aw <- x2y.beta.CI.high - x2y.beta.CI.low
      x3y.beta.aw <- x3y.beta.CI.high - x3y.beta.CI.low
      x4y.beta.aw <- x4y.beta.CI.high - x4y.beta.CI.low
      
      # BIAS
      x1y.beta.bias <- x1y.beta - truedata.fit.x1y["BMI"]
      x2y.beta.bias <- x2y.beta - truedata.fit.x2y["BMI"]
      x3y.beta.bias <- x3y.beta - truedata.fit.x3y["BMI"]
      x4y.beta.bias <- x4y.beta - truedata.fit.x4y["BMI"]
      
      
      # Coverage rate
      x1y.beta.coverage <- x1y.beta.CI.low < truedata.fit.x1y["BMI"] & truedata.fit.x1y["BMI"] < x1y.beta.CI.high
      x2y.beta.coverage <- x2y.beta.CI.low < truedata.fit.x2y["BMI"] & truedata.fit.x2y["BMI"] < x2y.beta.CI.high
      x3y.beta.coverage <- x3y.beta.CI.low < truedata.fit.x3y["BMI"] & truedata.fit.x3y["BMI"] < x3y.beta.CI.high
      x4y.beta.coverage <- x4y.beta.CI.low < truedata.fit.x4y["BMI"] & truedata.fit.x4y["BMI"] < x4y.beta.CI.high
   
   }

    # single imputation analysis
   else {
   
      mids <- complete(x, action = "all") #mids
      fit <- mids %>% map(~lm(BMI ~ Glucose + BloodPressure + SkinThickness + Insulin, data = .)) %>% .[[1]]
      summary <- summ(fit, confint = TRUE)
      
      
      #betas
      x1.beta <- fit$coefficients["Glucose"]
      x2.beta <- fit$coefficients["BloodPressure"]
      x3.beta <- fit$coefficients["SkinThickness"]
      x4.beta <- fit$coefficients["Insulin"]
   
      
      #standard errors
      x1.beta.se <- summary(fit)$coefficients[2,2]
      x2.beta.se <- summary(fit)$coefficients[3,2]
      x3.beta.se <- summary(fit)$coefficients[4,2]
      x4.beta.se <- summary(fit)$coefficients[5,2]
      
      #CI low 
      x1.beta.CI.low <- summary$coeftable[2,2]
      x2.beta.CI.low  <- summary$coeftable[3,2]
      x3.beta.CI.low  <- summary$coeftable[4,2]
      x4.beta.CI.low  <- summary$coeftable[5,2]
      
      #CI high
      x1.beta.CI.high <- summary$coeftable[2,3]
      x2.beta.CI.high  <- summary$coeftable[3,3]
      x3.beta.CI.high  <- summary$coeftable[4,3]
      x4.beta.CI.high  <- summary$coeftable[5,3]
  
      #bias
      x1.beta.bias <- x1.beta - truedata.fit["Glucose"]
      x2.beta.bias <- x2.beta - truedata.fit["BloodPressure"]
      x3.beta.bias <- x3.beta - truedata.fit["SkinThickness"]
      x4.beta.bias <- x4.beta - truedata.fit["Insulin"]
      
      #Aw
      x1.beta.aw <- x1.beta.CI.high - x1.beta.CI.low
      x2.beta.aw <- x2.beta.CI.high - x2.beta.CI.low
      x3.beta.aw <- x3.beta.CI.high - x3.beta.CI.low
      x4.beta.aw <- x4.beta.CI.high - x4.beta.CI.low
      
      #coverage 
      x1.beta.coverage <- x1.beta.CI.low < truedata.fit["Glucose"] & truedata.fit["Glucose"] < x1.beta.CI.high
      x2.beta.coverage <- x2.beta.CI.low < truedata.fit["BloodPressure"] & truedata.fit["BloodPressure"] < x2.beta.CI.high
      x3.beta.coverage <- x3.beta.CI.low < truedata.fit["SkinThickness"] & truedata.fit["SkinThickness"] < x3.beta.CI.high
      x4.beta.coverage <- x4.beta.CI.low < truedata.fit["Insulin"] & truedata.fit["Insulin"] < x4.beta.CI.high
       
      r.squared <- summary(fit)$r.squared
      
      #reversed models
      fit.x1y <- mids %>% map(~lm(Glucose ~ BMI + BloodPressure + SkinThickness + Insulin, data = .x)) %>% .[[1]]
      fit.x2y <- mids %>% map(~lm(BloodPressure ~ Glucose + BMI + SkinThickness + Insulin, data = .x)) %>% .[[1]]
      fit.x3y <- mids %>% map(~lm(SkinThickness ~ Glucose + BloodPressure + BMI + Insulin, data = .x)) %>% .[[1]]
      fit.x4y <- mids %>% map(~lm(Insulin ~ Glucose + BloodPressure + SkinThickness + BMI, data = .x)) %>% .[[1]]
      
      #summaries
      summary.x1y <- summ(fit.x1y, confint = TRUE)
      summary.x2y <- summ(fit.x2y, confint = TRUE)
      summary.x3y <- summ(fit.x3y, confint = TRUE)
      summary.x4y <- summ(fit.x4y, confint = TRUE)

      #betas
      x1y.beta <- fit.x1y$coefficients["BMI"]
      x2y.beta <- fit.x2y$coefficients["BMI"]
      x3y.beta <- fit.x3y$coefficients["BMI"]
      x4y.beta <- fit.x4y$coefficients["BMI"]
      
      #standard errors
      x1y.beta.se <- summary(fit.x1y)$coefficients[2,2]
      x2y.beta.se <- summary(fit.x2y)$coefficients[3,2]
      x3y.beta.se <- summary(fit.x3y)$coefficients[4,2]
      x4y.beta.se <- summary(fit.x4y)$coefficients[5,2]
   
      #CI low 
      x1y.beta.CI.low <- summary.x1y$coeftable[2,2]
      x2y.beta.CI.low  <- summary.x2y$coeftable[3,2]
      x3y.beta.CI.low  <- summary.x3y$coeftable[4,2]
      x4y.beta.CI.low  <- summary.x4y$coeftable[5,2]
      
      #CI high
      x1y.beta.CI.high <- summary.x1y$coeftable[2,3]
      x2y.beta.CI.high  <- summary.x2y$coeftable[3,3]
      x3y.beta.CI.high  <- summary.x3y$coeftable[4,3]
      x4y.beta.CI.high  <- summary.x4y$coeftable[5,3]
  
      #bias
      x1y.beta.bias <- x1y.beta - truedata.fit.x1y["BMI"]
      x2y.beta.bias <- x2y.beta - truedata.fit.x2y["BMI"]
      x3y.beta.bias <- x3y.beta - truedata.fit.x3y["BMI"]
      x4y.beta.bias <- x4y.beta - truedata.fit.x4y["BMI"]
      
      # aw
      x1y.beta.aw <- x1y.beta.CI.high - x1y.beta.CI.low
      x2y.beta.aw <- x2y.beta.CI.high - x2y.beta.CI.low
      x3y.beta.aw <- x3y.beta.CI.high - x3y.beta.CI.low
      x4y.beta.aw <- x4y.beta.CI.high - x4y.beta.CI.low
      
      #coverage 
      x1y.beta.coverage <- x1y.beta.CI.low < truedata.fit.x1y["BMI"] & truedata.fit.x1y["BMI"] < x1y.beta.CI.high
      x2y.beta.coverage <- x2y.beta.CI.low < truedata.fit.x2y["BMI"] & truedata.fit.x2y["BMI"] < x2y.beta.CI.high
      x3y.beta.coverage <- x3y.beta.CI.low < truedata.fit.x3y["BMI"] & truedata.fit.x3y["BMI"] < x3y.beta.CI.high
      x4y.beta.coverage <- x4y.beta.CI.low < truedata.fit.x4y["BMI"] & truedata.fit.x4y["BMI"] < x4y.beta.CI.high

   }
      
    return(c(  x1.beta, x1.beta.se, x1.beta.bias, x1.beta.aw, x1.beta.coverage, r.squared,
               x2.beta, x2.beta.se, x2.beta.bias, x2.beta.aw, x2.beta.coverage,
               x3.beta, x3.beta.se, x3.beta.bias, x3.beta.aw, x3.beta.coverage,
               x4.beta, x4.beta.se, x4.beta.bias, x4.beta.aw, x4.beta.coverage,
               x1y.beta, x1y.beta.se, x1y.beta.bias, x1y.beta.aw, x1y.beta.coverage,
               x2y.beta, x2y.beta.se, x2y.beta.bias, x2y.beta.aw, x2y.beta.coverage, 
               x3y.beta, x3y.beta.se, x3y.beta.bias, x3y.beta.aw, x3y.beta.coverage, 
               x4y.beta, x4y.beta.se, x4y.beta.bias, x4y.beta.aw, x4y.beta.coverage))
} 

format.p <- (c("x1.beta" = 0, "x1.beta.se" = 0, "x1.beta.bias" = 0, "x1.beta.aw" = 0, "x1.beta.coverage" = T, "r.squared" = 0,
               "x2.beta" = 0, "x2.beta.se" = 0, "x2.beta.bias" = 0, "x2.beta.aw" = 0, "x2.beta.coverage" = T,
               "x3.beta" = 0, "x3.beta.se" = 0, "x3.beta.bias" = 0, "x3.beta.aw" = 0, "x3.beta.coverage" = T,
               "x4.beta" = 0, "x4.beta.se" = 0, "x4.beta.bias" = 0, "x4.beta.aw" = 0, "x4.beta.coverage" = T,
          
               "x1y.beta" = 0, "x1y.beta.se" = 0, "x1y.beta.bias" = 0, "x1y.beta.aw" = 0, "x1y.beta.coverage" = T,
               "x2y.beta" = 0, "x2y.beta.se" = 0, "x2y.beta.bias" = 0, "x2y.beta.aw" = 0, "x2y.beta.coverage" = T, 
               "x3y.beta" = 0, "x3y.beta.se" = 0, "x3y.beta.bias" = 0, "x3y.beta.aw" = 0, "x3y.beta.coverage" = T, 
               "x4y.beta" = 0, "x4y.beta.se" = 0, "x4y.beta.bias" = 0, "x4y.beta.aw" = 0, "x4y.beta.coverage" = T))



```




