---
title: "5. Results"
author: "Boy Remmelzwaal"
date: "7/1/2021"
output: html_document
---

In this document you can find the code used for the results of the simulations.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(mice)
library(dplyr)
library(magrittr)
library(readr)
library(purrr)
library(mvtnorm)
library(tidyr)
library(tibble)
library(ggplot2)
library(reshape2)
library(gridExtra)

```

# Function: summarise RMSE
```{r}

grab.rmse <- function(x){
   
mean.y <-  x %>% map("rmse.mean.y") %>% as.data.frame() %>% t()
mean.x1 <- x %>% map("rmse.mean.x1") %>% as.data.frame() %>% t()
mean.x2 <- x %>% map("rmse.mean.x2") %>% as.data.frame() %>% t()
mean.x3 <- x %>% map("rmse.mean.x3") %>% as.data.frame() %>% t()
mean.x4 <- x %>% map("rmse.mean.x4") %>% as.data.frame() %>% t()
results.mean <- data.frame(y = mean.y, x1 = mean.x1, x2 = mean.x2, x3 = mean.x3, x4 = mean.x4) %>% cbind(., method='mean')

reg.y <-  x %>% map("rmse.reg.y") %>% as.data.frame() %>% t()
reg.x1 <- x %>% map("rmse.reg.x1") %>% as.data.frame() %>% t()
reg.x2 <- x %>% map("rmse.reg.x2") %>% as.data.frame() %>% t()
reg.x3 <- x %>% map("rmse.reg.x3") %>% as.data.frame() %>% t()
reg.x4 <- x %>% map("rmse.reg.x4") %>% as.data.frame() %>% t()
results.reg <- data.frame(y = reg.y, x1 = reg.x1, x2 = reg.x2, x3 = reg.x3, x4 = reg.x4) %>% cbind(., method='reg')

stochm1.y <-  x %>% map("rmse.stochm1.y") %>% as.data.frame() %>% t()
stochm1.x1 <- x %>% map("rmse.stochm1.x1") %>% as.data.frame() %>% t()
stochm1.x2 <- x %>% map("rmse.stochm1.x2") %>% as.data.frame() %>% t()
stochm1.x3 <- x %>% map("rmse.stochm1.x3") %>% as.data.frame() %>% t()
stochm1.x4 <- x %>% map("rmse.stochm1.x4") %>% as.data.frame() %>% t()
results.stochm1 <- data.frame(y = stochm1.y, x1 = stochm1.x1, x2 = stochm1.x2, x3 = stochm1.x3, x4 = stochm1.x4) %>% cbind(., method='stochm1')

stochm5.y <-  x %>% map("rmse.stochm5.y") %>% as.data.frame() %>% t()
stochm5.x1 <- x %>% map("rmse.stochm5.x1") %>% as.data.frame() %>% t()
stochm5.x2 <- x %>% map("rmse.stochm5.x2") %>% as.data.frame() %>% t()
stochm5.x3 <- x %>% map("rmse.stochm5.x3") %>% as.data.frame() %>% t()
stochm5.x4 <- x %>% map("rmse.stochm5.x4") %>% as.data.frame() %>% t()
results.stochm5 <- data.frame(y = stochm5.y, x1 = stochm5.x1, x2 = stochm5.x2, x3 = stochm5.x3, x4 = stochm5.x4) %>% cbind(., method='stochm5')

bayesm1.y <-  x %>% map("rmse.bayesm1.y") %>% as.data.frame() %>% t()
bayesm1.x1 <- x %>% map("rmse.bayesm1.x1") %>% as.data.frame() %>% t()
bayesm1.x2 <- x %>% map("rmse.bayesm1.x2") %>% as.data.frame() %>% t()
bayesm1.x3 <- x %>% map("rmse.bayesm1.x3") %>% as.data.frame() %>% t()
bayesm1.x4 <- x %>% map("rmse.bayesm1.x4") %>% as.data.frame() %>% t()
results.bayesm1 <- data.frame(y = bayesm1.y, x1 = bayesm1.x1, x2 = bayesm1.x2, x3 = bayesm1.x3, x4 = bayesm1.x4) %>% cbind(., method='bayesm1')

bayesm5.y <-  x %>% map("rmse.bayesm5.y") %>% as.data.frame() %>% t()
bayesm5.x1 <- x %>% map("rmse.bayesm5.x1") %>% as.data.frame() %>% t()
bayesm5.x2 <- x %>% map("rmse.bayesm5.x2") %>% as.data.frame() %>% t()
bayesm5.x3 <- x %>% map("rmse.bayesm5.x3") %>% as.data.frame() %>% t()
bayesm5.x4 <- x %>% map("rmse.bayesm5.x4") %>% as.data.frame() %>% t()
results.bayesm5 <- data.frame(y = bayesm5.y, x1 = bayesm5.x1, x2 = bayesm5.x2, x3 = bayesm5.x3, x4 = bayesm5.x4) %>% cbind(., method='bayesm5')

pmmm1.y <-  x %>% map("rmse.pmmm1.y") %>% as.data.frame() %>% t()
pmmm1.x1 <- x %>% map("rmse.pmmm1.x1") %>% as.data.frame() %>% t()
pmmm1.x2 <- x %>% map("rmse.pmmm1.x2") %>% as.data.frame() %>% t()
pmmm1.x3 <- x %>% map("rmse.pmmm1.x3") %>% as.data.frame() %>% t()
pmmm1.x4 <- x %>% map("rmse.pmmm1.x4") %>% as.data.frame() %>% t()
results.pmmm1 <- data.frame(y = pmmm1.y, x1 = pmmm1.x1, x2 = pmmm1.x2, x3 = pmmm1.x3, x4 = pmmm1.x4) %>% cbind(., method='pmmm1')

pmmm5.y <-  x %>% map("rmse.pmmm5.y") %>% as.data.frame() %>% t()
pmmm5.x1 <- x %>% map("rmse.pmmm5.x1") %>% as.data.frame() %>% t()
pmmm5.x2 <- x %>% map("rmse.pmmm5.x2") %>% as.data.frame() %>% t()
pmmm5.x3 <- x %>% map("rmse.pmmm5.x3") %>% as.data.frame() %>% t()
pmmm5.x4 <- x %>% map("rmse.pmmm5.x4") %>% as.data.frame() %>% t()
results.pmmm5 <- data.frame(y = pmmm5.y, x1 = pmmm5.x1, x2 = pmmm5.x2, x3 = pmmm5.x3, x4 = pmmm5.x4) %>% cbind(., method='pmmm5')

longformat_results <- rbind(results.mean, results.reg, results.stochm1, results.stochm5, results.bayesm1, results.bayesm5, results.pmmm1, results.pmmm5)

  return(longformat_results)
}

#Grabbing the results for every missingness scenario
rmse.10 <- grab.rmse(result.p10)
rmse.25 <- grab.rmse(result.p25)
rmse.50 <- grab.rmse(result.p50)


```


# Result: Average RMSE per method for 10% missingness scenario
```{r}
rmse.10 %>% split(.$method) %>% map(summary)

```

# Result: Average RMSE per method for 25% missingness scenario
```{r}
rmse.25 %>% split(.$method) %>% map(summary)
```

# Result: Average RMSE per method for 50% missingness scenario
```{r}
rmse.50 %>% split(.$method) %>% map(summary)
```




# Results: Regression coefficents 10% missingenss - Boostrap SE, bias, CIW and coverage rates.
```{r, warning=FALSE}

mean10 <- result.p10 %>% 
  map("imp.mean") %>% 
  grab.it.single() %>% round(4)
mean10

reg10 <- result.p10 %>% 
  map("imp.reg") %>% 
  grab.it.single()  %>% round(4)
reg10

stoch.m1.10 <- result.p10 %>% 
  map("imp.stoch.m1") %>% 
  grab.it.single()  %>% round(4)
stoch.m1.10

bayes.m1.10 <- result.p10 %>% 
  map("imp.bayes.m1") %>% 
  grab.it.single()  %>% round(4)
bayes.m1.10

pmm.m1.10 <- result.p10 %>% 
  map("imp.pmm.m1") %>% 
  grab.it.single()  %>% round(4)
pmm.m1.10

stoch.m5.10 <- result.p10 %>% 
  map("imp.stoch.m5") %>% 
  grab.it()  %>% round(4)
stoch.m5.10

bayes.m5.10 <- result.p10 %>% 
  map("imp.bayes.m5") %>% 
  grab.it()  %>% round(4)
bayes.m5.10

pmm.m5.10 <- result.p10 %>% 
  map("imp.pmm.m5") %>% 
  grab.it()  %>% round(4)
pmm.m5.10
```

# Results: Regression coefficents 25% missingenss - Boostrap SE, bias, CIW and coverage rates.
```{r, warning=FALSE}
mean25 <- result.p25 %>% 
  map("imp.mean") %>% 
  grab.it.single() %>% round(4)
mean25

reg25 <- result.p25 %>% 
  map("imp.reg") %>% 
  grab.it.single() %>% round(4)
reg25

stoch.m1.25 <- result.p25 %>% 
  map("imp.stoch.m1") %>% 
  grab.it.single() %>% round(4)
stoch.m1.25

bayes.m1.25 <- result.p25 %>% 
  map("imp.bayes.m1") %>% 
  grab.it.single() %>% round(4)
bayes.m1.25

pmm.m1.25 <- result.p25 %>% 
  map("imp.pmm.m1") %>% 
  grab.it.single() %>% round(4)
pmm.m1.25

stoch.m5.25 <- result.p25 %>% 
  map("imp.stoch.m5") %>% 
  grab.it() %>% round(4)
stoch.m5.25

bayes.m5.25 <- result.p25 %>% 
  map("imp.bayes.m5") %>% 
  grab.it()  %>% round(4)
bayes.m5.25

pmm.m5.25 <- result.p25 %>% 
  map("imp.pmm.m5") %>% 
  grab.it()  %>% round(4)
pmm.m5.25
```

# Results: Regression coefficents 50% missingenss - Boostrap SE, bias, CIW and coverage rates.
```{r, warning=FALSE}

mean50 <- result.p50 %>% 
  map("imp.mean") %>% 
  grab.it.single() %>% round(4)
mean50

reg50 <- result.p50 %>% 
  map("imp.reg") %>% 
  grab.it.single() %>% round(4)
reg50

stoch.m1.50 <- result.p50 %>% 
  map("imp.stoch.m1") %>% 
  grab.it.single() %>% round(4)
stoch.m1.50

bayes.m1.50 <- result.p50 %>% 
  map("imp.bayes.m1") %>% 
  grab.it.single() %>% round(4)

pmm.m1.50 <- result.p50 %>% 
  map("imp.pmm.m1") %>% 
  grab.it.single() %>% round(4)
pmm.m1.50

stoch.m5.50 <- result.p50 %>% 
  map("imp.stoch.m5") %>% 
  grab.it() %>% round(4)
stoch.m5.50

bayes.m5.50 <- result.p50 %>% 
  map("imp.bayes.m5") %>% 
  grab.it() %>% round(4)
bayes.m5.50

pmm.m5.50 <- result.p50 %>% 
  map("imp.pmm.m5") %>% 
  grab.it() %>% round(4)
pmm.m5.50
```

# Results: Summary of reverse model regression coefficients.
```{r}

statistics_summary_p <- function(x){

# True data
data <-  x %>% map("data") %>% vapply(., true.estimates.p, format.p) %>% t()
data <- colMeans(data) 

# imp mean
mean <- x %>% map("imp.mean") %>% vapply(., statistics.p, format.p) %>% t()
mean <- colMeans(mean)

reg <- x %>% map("imp.reg") %>% vapply(., statistics.p, format.p) %>% t()
reg <- colMeans(reg)
  
stoch.m1 <- x %>% map("imp.stoch.m1") %>% vapply(., statistics.p, format.p) %>% t()
stoch.m1 <- colMeans(stoch.m1)

stoch.m5 <- x %>% map("imp.stoch.m5") %>% vapply(., statistics.p, format.p) %>% t()
stoch.m5 <- colMeans(stoch.m5)

bayes.m1 <- x %>% map("imp.bayes.m1") %>% vapply(., statistics.p, format.p) %>% t()
bayes.m1 <- colMeans(bayes.m1)

bayes.m5 <- x %>% map("imp.bayes.m5") %>% vapply(., statistics.p, format.p) %>% t()
bayes.m5 <- colMeans(bayes.m5)

pmm.m1 <- x %>% map("imp.pmm.m1") %>% vapply(., statistics.p, format.p) %>% t()
pmm.m1 <- colMeans(pmm.m1)

pmm.m5 <- x %>% map("imp.pmm.m5") %>% vapply(., statistics.p, format.p) %>% t()
pmm.m5 <- colMeans(pmm.m5)

  return(rbind(data, mean, reg, stoch.m1, stoch.m5, bayes.m1, bayes.m5, pmm.m1, pmm.m5))
}

#50% missingness
final_result_p50 <- statistics_summary_p(result.p50)

#25% missingness
final_result_p25 <- statistics_summary_p(result.p25) 

#10% missingness
final_result_p10 <- statistics_summary_p(result.p10) 



```

# Results: Descriptives - summary wide format
```{r}

statistics_summary_d <- function(x){
  
# True data
data <- x %>% map("data") %>% vapply(., true.estimates.d, format.d) %>% t()
data <- colMeans(data) 

# imp mean
mean <- x %>% map("imp.mean") %>% vapply(., statistics.d, format.d) %>% t()
mean <- colMeans(mean)

reg <- x %>% map("imp.reg") %>% vapply(., statistics.d, format.d) %>% t()
reg <- colMeans(reg)
  
stoch.m1 <- x %>% map("imp.stoch.m1") %>% vapply(., statistics.d, format.d) %>% t()
stoch.m1 <- colMeans(stoch.m1)

stoch.m5 <- x %>% map("imp.stoch.m5") %>% vapply(., statistics.d, format.d) %>% t()
stoch.m5 <- colMeans(stoch.m5)

bayes.m1 <- x %>% map("imp.bayes.m1") %>% vapply(., statistics.d, format.d) %>% t()
bayes.m1 <- colMeans(bayes.m1)

bayes.m5 <- x %>% map("imp.bayes.m5") %>% vapply(., statistics.d, format.d) %>% t()
bayes.m5 <- colMeans(bayes.m5)

pmm.m1 <- x %>% map("imp.pmm.m1") %>% vapply(., statistics.d, format.d) %>% t()
pmm.m1 <- colMeans(pmm.m1)

pmm.m5 <- x %>% map("imp.pmm.m5") %>% vapply(., statistics.d, format.d) %>% t()
pmm.m5 <- colMeans(pmm.m5)

  return(rbind(data, mean, reg, stoch.m1, stoch.m5, bayes.m1, bayes.m5, pmm.m1, pmm.m5))
}


final_result_d10 <- statistics_summary_d(result.p10) 
final_result_d25 <- statistics_summary_d(result.p25) 
final_result_d50 <- statistics_summary_d(result.p50) 


```


